Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-05-31 paper_jasa.tex
model notation updated
notation suggestion

\red{Here is what my suggestion for notation \\  Use $B$ for logistic model and $\beta$ for linear model \\ Use $X$ to indicate logistic model covariate matrix and $Y$ to indicate binomial random variable since it is a kind of response. \\ Use $\pi_i$ instead of $p_i$ since $p_i$ is used for p-vaue.}

>>>>

\red{Here is what my suggestion for notation \\  Use $B$ for logistic model and $\beta$ for linear model \\ Use $X$ to indicate logistic model covariate matrix and $U$ to denote binomial variable \\ $Y$ to indicate observed data. \\ Use $\pi_i$ instead of $p_i$ since $p_i$ is used for p-value.  \\ Should I change everything accordingly? }
